---
title: "Example usage or rawTof"
author: "Clemens Ager"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette shows how to load the sample PTR data provided by
Ionicon.

The package requires [rhdf5](https://bioconductor.org/packages/release/bioc/html/rhdf5.html).
```{r library}
library(rhdf5)
```

## Opening a TOF file

```{r opening a tof file}
tof.h5 <- "extdata/PTRTOF_test_spectrum.h5"
fid <- H5Fopen(tof.h5)
```

```{r}
peaktable <- get_peak_matrix(fid)
plot(peaktable[69, ], type="l")
plot(peaktable[45, ], type="l")

mh <- masscal_helper(fid)
ss <- get_sum_spec(fid)/180
s2 <- get_single_scan(fid, 31)
mass_scale <- mh$to_mass(seq_along(ss))
plot(mass_scale, s2, type="l")
lines(mass_scale, ss, col="red")

mass_range <- mh$to_index(c(40, 50))
selected <- seq(from = floor(mass_range[1]),
                to = ceiling(mass_range[2]))

plot(mass_scale[selected], s2[selected], type="l")
lines(mass_scale[selected], ss[selected], col="red")
```



## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
